environmental_data_preperation

### 2018-09-10 src/environmental_data_preperation.Rmd
wel...not really much progress..

# Package dependencies
You can load them using the following code which uses a function called [ipak](https://gist.github.com/stevenworthington/3178163). 
Note this function checks to see if the packages are installed first.
Th
```{r pre-install packages, message=FALSE}
packages <- c("RNetCDF", "raster")
source("./src/ipak.R")
ipak(packages)
suppressMessages(ipak)
```

# read in a netcdf
```{r}
library("RNetCDF") #this will read the netcdf version 1 formats 
library(ncdf4)
ncbr <- brick("../data/env/CMEMS_GLOBAL_REANALYSIS_PHY_001_025_salinity_monthly_mean_1993-01.nclonlat.ncdepthtrim.nc")
ncbr
```

reproject...
```{r}
canada_eq_ar_proj <- "+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"
library(rgdal)
rp <- projectRaster(ncbr, crs = canada_eq_ar_proj)
rp
```

>>>>

# Package dependencies
You can load them using the following code which uses a function called [ipak](https://gist.github.com/stevenworthington/3178163). 
Note this function checks to see if the packages are installed first.
Th
```{r pre-install packages, message=FALSE}
packages <- c("RNetCDF", "raster", "rgdal")
source("./src/ipak.R")
ipak(packages)
suppressMessages(ipak)
```

# read in a netcdf
```{r}
library("RNetCDF") #this will read the netcdf version 1 formats 
library("ncdf4")
ncbr <- brick("../data/env/CMEMS_GLOBAL_REANALYSIS_PHY_001_025_salinity_monthly_mean_1993-01.nclonlat.ncdepthtrim.nc")
ncbr
```

reproject...
```{r}
canada_eq_ar_proj <- "+proj=aea +lat_1=50 +lat_2=70 +lat_0=40 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"
library("rgdal")
rp <- projectRaster(ncbr, crs = canada_eq_ar_proj)
rp
```
